The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-06-06 SIR_manuscript.tex
collapse of G to R0

%%%%%%%%%%%%

\section{Discussion}

In this paper, we have defined and analyzed a simple compartmental model that combines epidemiological dynamics (as defined by a simple SIR model) with the dynamics of testing and isolation. Our model is a caricature --- it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g. exposed, presymptomatic, and asymptomatic compartments [REFS]; time-varying testing rates [REFS?]; behavioural dynamics [REF Weitz/Park/Dushoff]). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.

Many of the qualitative results we have derived are mathematical confirmations of simple, common-sense intuitions. In particular, we can decrease $\Rnum$ by increasing isolation efficacy or testing intensity; returning tests faster, if individuals do not isolate while they are waiting for results; or increasing testing focus to target individuals who are likely to be infectious (e.g. symptomatic people or close contacts of known infections).

>>>>

%%%%%%%%%%%%
\section{Discussion}

### 2021-06-06 cohort.tex
minor change
collapse of G to R0

\theoremstyle{definition} % amsthm only
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}

@@

\item
Calculating the next-generation vector $\vec G$ is 
(\ali{feels odd here, help! $\vec G$ here is a vector with elements of the eigenvalues of the \citep{van2002reproduction}'s next-generation matrix $FV^{-1}$. 
Also check Heesterbeek work what he calls this}) 
\begin{equation}
\label{eq:ng} %next generation
\vec G = FV^{-1} = \int_0^\infty \vec K(\tau) d\tau.
\end{equation}
Note that $\R$ would be the dominant element of $\vec G$.
\end{enumerate}
Note that in the compartment framework \cite{van2002reproduction}, steps 2 and 3 are combined.

@@

{\it Step 1;} The cohort Eq.~ is
\begin{align}
\vec I'=-V\,\vec I,~~ \text{where}~~ \vec I(\tau)=\left[ \begin {array}{c} I\_u(\tau)\\I_n(\tau)\\I_p(\tau)\\I_c(\tau) \end {array} \right], ~~
\vec I(0)=\left[ \begin {array}{c} S\_u^*\\S\_n^*\\0\\0 \end {array} \right].
\end{align}
Solving for $\vec I(\tau)$ by finding the eigenvalues and eigenvectors of the above linear system results in
\begin{align}
\vec I(\tau)=&
c_1\,\exp(-\gamma\,\tau)\,\left[ \begin {array}{c} 0\\0\\0\\1 \end {array} \right] 
+c_2\,\exp(-(F_I+\gamma)\,\tau)\,\left[ \begin {array}{c} \frac{F_I-\omega}{\omega}\\0\\\frac{-F_I}{\omega}\\1 \end {array} \right]
+c_3\,\exp(-(\omega+\gamma)\,\tau)\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right] \\\notag
+& c_4\,\exp(-(\omega+\gamma)\,\tau)\,\Big(\tau\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right]+
\left[ \begin {array}{c} \frac{-1}{F_I}\\ \frac{\omega-F_I}{F_I\,\omega}\\ \frac{1}{\omega}\\0 \end {array} \right]\Big),
\end{align}
where 
\begin{align}
c_1=&1\\
c_2=&\frac{\omega}{F_I-\omega}(S\_u^*-\frac{\omega}{F_I-\omega}\,S\_n^*)\\
c_3=&\frac{-F_I}{F_I-\omega}(1-\frac{\omega}{F_I-\omega}S\_n^*)\\
c_4=&\frac{-\omega\,F_I}{F_I-\omega}S\_n^*.
\end{align}

>>>>

\theoremstyle{definition} % amsthm only
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{note}{Note}

@@

\item
Calculating the next-generation vector $\vec G$ is 
(\ali{feels odd here, help! $\vec G$ here is a vector with elements of the eigenvalues of the \citep{van2002reproduction}'s next-generation matrix $FV^{-1}$. 
Also check Heesterbeek work what he calls this}) 
\begin{equation}
\label{eq:ng} %next generation
\vec G = FV^{-1} \vec I(0)= \int_0^\infty \vec K(\tau) d\tau.
\end{equation}
Note that $\R$ would be the dominant element of $\vec G$.
\end{enumerate}

\begin{note}
The following notes/points are to be considered in moving from one framework to another, namely, cohort framework \citep{champredon2018equivalence} and comartmental framework \citep{van2002reproduction}; 
\begin{enumerate}
\item
In the compartment framework, steps 2 and 3 are combined.
\item
If the initial condition $\vec I(0)$ of the cohort Eq.~\eqref{eq:I} (in the cohort framework) is chosen as the principal eigenvector of the next-generation matrix $FV^{-1}$ corresponding to $\R$ (in compartmental framework), the next generation vector $\vec G$~\eqref{eq:ng} would be 
\begin{equation}
\vec G = FV^{-1} \vec I(0) = \R \vec I(0).
\end{equation}
Thus, in this case inorder to collapse $\vec G$ to $\R$, if $\vec I(0)$ is a unit vector as well, i.e., $\lVert \vec I(0) \rVert = 1$, it follows that $\vec I(0)^t \cdot \vec G = \R$, where $\vec I(0)^t$ is the transpose of $\vec I(0)$.
\end{enumerate}
\end{note}

@@

{\it Step 1;} The cohort Eq.~ is
\begin{align}
\vec I'=-V\,\vec I,~~ \text{where}~~ \vec I(\tau)=\left[ \begin {array}{c} I\_u(\tau)\\I_n(\tau)\\I_p(\tau)\\I_c(\tau) \end {array} \right], ~~
\vec I(0)=\left[ \begin {array}{c} S\_u^*\\(1-\theta\_w)S\_n^*\\0\\0 \end {array} \right].
\end{align}
Solving for $\vec I(\tau)$ by finding the eigenvalues and eigenvectors of the above linear system results in
\begin{align}
\vec I(\tau)=&
c_1\,\exp(-\gamma\,\tau)\,\left[ \begin {array}{c} 0\\0\\0\\1 \end {array} \right] 
+c_2\,\exp(-(F_I+\gamma)\,\tau)\,\left[ \begin {array}{c} \frac{F_I-\omega}{\omega}\\0\\\frac{-F_I}{\omega}\\1 \end {array} \right]
+c_3\,\exp(-(\omega+\gamma)\,\tau)\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right] \\\notag
+& c_4\,\exp(-(\omega+\gamma)\,\tau)\,\Big(\tau\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right]+
\left[ \begin {array}{c} \frac{-1}{F_I}\\ \frac{\omega-F_I}{F_I\,\omega}\\ \frac{1}{\omega}\\0 \end {array} \right]\Big),
\end{align}
where 
\begin{align}
c_1=&1\\
c_2=&\frac{\omega}{F_I-\omega}(S\_u^*-\frac{\omega}{F_I-\omega}\,S\_n^*)\\
c_3=&\frac{-F_I}{F_I-\omega}(1-\frac{\omega}{F_I-\omega}S\_n^*)\\
c_4=&\frac{-\omega\,F_I}{F_I-\omega}S\_n^*.
\end{align}
